\documentclass[12pt, a4paper, oneside,UTF8]{ctexart}
\usepackage{amsmath, amsthm, amssymb, bm, color, framed, graphicx, hyperref, mathrsfs,amsfonts}
\usepackage[left=1.0cm,right=1.0cm,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage{booktabs,multirow,tabularray}%表格使用，转换使用excel插件
\usepackage{pgf-pie}%饼图使用
%\linespread{1.5}
\definecolor{shadecolor}{cmyk}{0.09,0.63,0,0.51}
% \definecolor{NJUblue}{cmyk}{0.09,0.63,0,0.51}
\newcounter{problemname}
\newenvironment{problem}{\stepcounter{problemname}\par\noindent\textbf{题目\arabic{problemname}. }}{\par}
\newenvironment{solution}{\begin{shaded}\par\noindent\textbf{解答. }}{$\Box$\end{shaded}\par}
\newenvironment{note}{\par\noindent\textbf{题目\arabic{problemname}的注记. }}{\par}
\ctexset{ section = { format={\Large \bfseries } } }
\DeclareMathOperator{\st}{s.t.}
\renewcommand{\familydefault}{\rmdefault} %可选择\rmdefault \sfdefault \ttdefault 分别是罗马字体，sans-serif字体和等宽字体  \familydefault是默认字体

\title{讲稿}
\author{李冠霖 221502012}
\date{\today}
\begin{document}
\maketitle
\tableofcontents
\newpage
Green Brothers Grimm, the German authors of the famous book called “Green Brothers Grimm’s Tales”, are the brothers Jacob and Wilhelm Grimm.
They were born in 1785 and 1786 respectively in Göttingen, the capital of Baden.
They were both poets, historians, and tales collectors at the age of twelve. After completing their studies, they went to work for a time in their father’s various jobs.
In 1806, they opened a successful brewing shop in their hometown of Göttingen.
The success of the shop encouraged the brothers to continue their literary work. 
In 1808, they published the first collection of folk tales, called “Deutsche Märchen”, which quickly became a best-seller.
This collection contained a great number of tales about the gods, heroes, and other ancient figures of the Germanic race.
In 1812, the brothers published the second edition of “Deutsche Märchen”. This time, they added many new tales to the collection.
Later on, they added new tales to the collection every year until they published the forty-seventh and final edition in 1812, which is known as the “Jahrbuch”.
The “Jahrbuch” is still the best-selling book in the German-speaking world.Each year, new editions are published to keep up with the demand for the collection. 
The collection contains many classics of German folk literature, such as “The Tales of Hansel and Gretel”, “The Simple Simon”, “One Thousand and One Nights”, “The Legend of the Magician”, and “The Well of the Magician”.
The Green Brothers Grimm have been regarded as the founders of the genre of children’s literature in Germany. 
Their books have been translated into many languages and are loved and read by children all over the world.

% \begin{tikzpicture}
%     \pie[text=legend]{10/A, 20/B, 30/C, 40/D}
%     \pie[text=pin,pos={8,0},explode=0.1]{20/A, 30/B, 40/C, 10/D}
% \end{tikzpicture}
\end{document}